Tools and Ideas for the Proceedural Generation of Shadow Sculptures.

### 2015-12-15 paper/paper.tex
Change font used when describing files and git branches.

The first method is partially implemented in the file `rayTracing.py' on the branch `master' in the submitted git repository \cite{gitrepo}. In this method the cast shadow of each sphere and cylinder is computed individually and merged. Here is some pseudo-code for rendering the shadow of a collection of spheres and cylinders illuminated by a single point light source:

@@

In an attempt to render shadows more quickly, another technique was attempted. The code for this technique can be found in the newRayTracing branch of the git repository. This second method is a refinement of the following naive method:

>>>>

The first method is partially implemented in the file \texttt{rayTracing.py} on the branch \texttt{master} in the submitted git repository \cite{gitrepo}. In this method the cast shadow of each sphere and cylinder is computed individually and merged. Here is some pseudo-code for rendering the shadow of a collection of spheres and cylinders illuminated by a single point light source:

@@

In an attempt to render shadows more quickly, another technique was attempted. The code for this technique can be found in the \texttt{newRayTracing} branch of the git repository in the file \texttt{rayTracing.py}. This second method is a refinement of the following naive method:
